Thoughts on resubmission within ARC1

### 2009-02-05 doc/client/resubmit_and_migrate_plans.tex
Additions to the technical implementation of the arcmigrate command

\documentclass[12pt,oneside,a4paper,english]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx,epic,eepic}
\usepackage{amssymb}
\usepackage{amsmath}

\title{Thoughts on resubmission within ARC1}
\author{Peter Rosendahl}

@@

\subsection*{Solutions}
In order to solve the scenarios mentioned above, we suggest to implement functionality on both server and client side to provide the commands \texttt{arcresume}, \texttt{arcmigrate} and \texttt{arcresub}.

@@

\subsection*{\texttt{arcmigrate}}
The \texttt{arcmigrate} command should enable users to move jobs from one cluster to another. In this first implementation the command will only support the migration of jobs which are queued in the batch system, i.e. there will be no support for check-pointing etc allowing for migration of running jobs. Nevertheless migration of queueing jobs is the foreseen most frequent use case, in which users would like to migrate queueing jobs from one cluster (computing element) to another cluster (computing element) which meanwhile have been freed or made available in other ways.

@@

\subsubsection*{Technical imlplementation:}

@@

\subsubsection*{Technical imlplementation:}

% Comments from Balazs:
%relate new job to the old one
%clarify what it means to be started
\end{document}

>>>>

\documentclass[11pt,oneside,a4paper,english]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx,epic,eepic}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{a4wide}
\usepackage{xspace}

\newcommand{\arcmigrate}{\texttt{arcmigrate}\xspace}

@@

\subsection*{Solutions}
In order to solve the scenarios mentioned above, we suggest to implement functionality on both server and client side to provide the commands \texttt{arcresume}, \arcmigrate and \texttt{arcresub}.

@@

\subsection*{\arcmigrate}
The \arcmigrate command should enable users to move jobs from one cluster to another. In this first implementation the command will only support the migration of jobs which are queued in the batch system, i.e. there will be no support for check-pointing etc allowing for migration of running jobs. Nevertheless migration of queueing jobs is the foreseen most frequent use case, in which users would like to migrate queueing jobs from one cluster (computing element) to another cluster (computing element) which meanwhile have been freed or made available in other ways.

@@

%% Edited by Martin Skou
\subsubsection*{Technical imlplementation:}
In a first implementation the \arcmigrate will only be able to migrate a queued job from an ARC1 cluster (old-cluster) to an ARC1 cluster (new-cluster). In its simplest invocation the command should take one argument specified by the user ie. the job id of a queued job on old-cluster. In case the job is not queued an error should be returned and the command should exit.

From the job id a migration specific JSDL file (migration-JSDL) is generated and used communicate with a possible new-cluster (candidate-cluster). For the migration-JSDL file extending JSDL was required.

Now clusters are contacted in the usual way and if a connection to a candidate cluster is accepted migration-JSDL is send.

From the received migration-JSDL, candidate-cluster fetches the JSDL file of the job (original-JSDL) which is located on old-cluster. Candidate-cluster then examine through original-JSDL if the job are able to run there. If positive, input files specified in original-JSDL should be fetched. If not candidate-cluster returns an error and the next cluster should be tried.

Input files can be divided in two categories: local files and storage element files. As default candidate-cluster should fetch local files from old-cluster while storage element files should be fetched from the storage element as this in general should be faster. If candidate-cluster succeeds in fetching the files the job is started at candidate-cluster now termed new-cluster.

Now the job on old-cluster should be killed. Two possible solutions exists. First solution is to let the client send a kill signal to old-cluster. And in the second solution the signal will be send from new-cluster. If the client should send the kill signal, new-cluster should return the new job-id after starting the job. While if new-cluster should send the signal, the job-id will be returned after sending the signal. In both cases, if the job cannot be killed a warning will be given.

@@

\subsubsection*{Technical imlplementation:}
\end{document}
